---
title: "Cool Spots in Ibadan, Nigeria"
author: "Motogg"
date: "October 6, 2016"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, comment = "")
```

## Cool Places in Ibadan
```{r leafletMap, echo=F}
library(leaflet)
locIcons = iconList(dominosIcon = makeIcon(iconUrl = "http://www.duskyillusions.com/wp-content/uploads/2015/02/Dominos_Logo.png",
          iconWidth = 31*2*215/230, iconHeight = 31*1.5,
          iconAnchorX = 31*215/230/2, iconAnchorY = 16)
,
dominosIcon = makeIcon(iconUrl = "http://www.duskyillusions.com/wp-content/uploads/2015/02/Dominos_Logo.png",
          iconWidth = 31*2*215/230, iconHeight = 31*1.5,
          iconAnchorX = 31*215/230/2, iconAnchorY = 16)
,
venturaIcon = makeIcon(iconUrl = "http://etc.usf.edu/presentations/extras/letters/varsity_letters/03/34/v-400.png",
      iconWidth = 31*215/230, iconHeight = 31,
      iconAnchorX = 31*215/230/2, iconAnchorY = 16)
, 
agodiIcon = makeIcon(iconUrl =                            "http://etc.usf.edu/presentations/extras/letters/varsity_letters/09/13/a-400.png",
      iconWidth = 31*215/230, iconHeight = 31,
      iconAnchorX = 31*215/230/2, iconAnchorY = 16)
,
heritageIcon = makeIcon(iconUrl = 
"http://etc.usf.edu/presentations/extras/letters/varsity_letters/01/20/h-400.png",
      iconWidth = 31*215/230, iconHeight = 31,
      iconAnchorX = 31*215/230/2, iconAnchorY = 16)
,
palmsIcon = makeIcon(iconUrl =                              "http://etc.usf.edu/presentations/extras/letters/varsity_letters/08/28/p-400.png",
      iconWidth = 31*215/230, iconHeight = 31,
      iconAnchorX = 31*215/230/2, iconAnchorY = 16)
)

sites_of_loc = c(  "<a href='http://www.dominos.ng/'>Domino's Pizza, Bodija, Ibadan</a>",
                   "<a href='http://www.dominos.ng/'>Domino's Pizza, Ring Road, Ibadan</a>",
                   "<a href='http://theventuramall.com/'>Ventura Mall, Samonda, Ibadan</a>",
                   "<a href='http://agodigardens.com/'>Agodi Gardens, Parliament Road, Ibadan</a>",
                   "<a href='https://www.google.com/search?client=safari&rls=en&q=heritage+mall+ibadan&ie=UTF-8&oe=UTF-8/'>Heritage Mall, Dugbe, Ibadan</a>",
                   "<a href='http://thepalmshoppingmall.com/ibadan/'>The Palms, Ring Road, Ibadan</a>")


df = data.frame(lat = c(7.417127, 7.368029, 7.427005, 7.406946, 7.386598, 7.364158), 
                lng = c(3.903273, 3.860300, 3.901823, 3.899265, 3.879874, 3.865799))

df %>%
        leaflet() %>%
        addTiles() %>%
        addMarkers(icon = locIcons , popup = sites_of_loc)
        
        